Forecasting the US Presidential Election: A Poll-of-Polls Approach Using Linear Models By Using Data of Pollsters From Five Thirty Eight In 2024

### 2024-10-22 paper/paper.qmd
merge paper.qmd update cleaned data
update appendix graph position

## SLR Model set-up

@@

modelsummary::modelsummary(
  MLR_models,
  fmt = 2
)
```
We first check the residual vs. fitted plot as shown in [Appendix @sec-model-details], and see no obvious violation of assumptions. According to the summary, DEM and REP models are based on the largest number of observations (both 1235). Smaller parties have fewer observations, which may lead to less robust models. The $r^2$ shows that the model explain the highest amount of variance on Democratic Party than others with value 0.357, and other parties less than 0.2. Based on the summary of models for DEM and REP [@tbl-mlrmodelsum], we are not sure if those predictor that measure quality of polls are significant or not, so we keep them for now in Bayesian model. Prediction of MLR models is shown in [@fig-mlrpredict], which we can see blue line which is Democratic party has a steeper slope and start to take the lead between day 100 and day 200.

@@

# Model details {#sec-model-details}
## Assumption check for MLR models
```{r}
#| eval: true
#| echo: false
#| message: false
#| warning: false
#| label: fig-assumptioncheck
#| layout-ncol: 2
#| fig-cap: "Examining how the model fits, and is affected by, the data"
#| fig-subcap: [""]

for (party in names(MLR_models)) {
  # Extract the model for the current party
  current_model <- MLR_models[[party]]

  # Create a Residuals vs Fitted plot for the current model
  plot(current_model, which = 1, main = paste("Residuals vs Fitted for", party, "Party"))

}
```

## Significant check for MLR models
```{r}
#| echo: false
#| eval: true
#| label: tbl-mlrmodelsum
#| tbl-cap: "Summary of DEM and REP data fit by MLR model"
#| warning: false

summary(MLR_models[['DEM']])
summary(MLR_models[['REP']])
```

## Posterior predictive check

```{r}
#| eval: true
#| echo: false
#| message: false
#| warning: false
#| label: fig-ppcheck
#| layout-ncol: 2
#| fig-cap: "Posterior prediction check for Bayesian model"

@@

@fig-stanareyouokay-1 is a trace plot. It shows... This suggests...

@fig-stanareyouokay-2 is a Rhat plot. It shows... This suggests...

>>>>

@@

modelsummary::modelsummary(
  MLR_models,
  fmt = 2
)
```
We first check the residual vs. fitted plot as shown in [Appendix @sec-model-details], and see no obvious violation of assumptions. According to the summary, DEM and REP models are based on the largest number of observations (both 1235). Smaller parties have fewer observations, which may lead to less robust models. The $r^2$ shows that the model explain the highest amount of variance on Democratic Party than others with value 0.357, and other parties less than 0.2. Based on the summary of models for DEM and REP [@sec-model-sigcheck], we are not sure if those predictor that measure quality of polls are significant or not, so we keep them for now in Bayesian model. Prediction of MLR models is shown in [@fig-mlrpredict], which we can see blue line which is Democratic party has a steeper slope and start to take the lead between day 100 and day 200.

@@

# Model details {#sec-model-details}
## Assumption check for MLR models
```{r}
#| echo: false
#| eval: true
#| warning: false
#| fig.cap: "Residuals vs Fitted for DEM Party"

plot(MLR_models[['DEM']], which = 1, main = "Residuals vs Fitted for DEM Party")
```

```{r}
#| echo: false
#| eval: true
#| warning: false
#| fig.cap: "Residuals vs Fitted for REP Party"

plot(MLR_models[['REP']], which = 1, main = "Residuals vs Fitted for REP Party")
```
## Significant check for MLR models {#sec-model-sigcheck}
see [@tbl-mlrmodelsum-dem], and [@tbl-mlrmodelsum-rep]
```{r}
#| echo: false
#| eval: true
#| label: tbl-mlrmodelsum-dem
#| tbl-cap: "Summary of DEM data fit by MLR model"
#| warning: false

summary(MLR_models[['DEM']])
```
```{r}
#| echo: false
#| eval: true
#| label: tbl-mlrmodelsum-rep
#| tbl-cap: "Summary of REP data fit by MLR model"
#| warning: false

summary(MLR_models[['REP']])
```

\newpage
## Posterior predictive check {#sec-model-ppcheck}

```{r}
#| eval: true
#| echo: false
#| message: false
#| warning: false
#| label: fig-ppcheck
#| fig-cap: "Posterior prediction check for Bayesian model"

@@

<!-- @fig-stanareyouokay-1 is a trace plot. It shows... This suggests... -->

<!-- @fig-stanareyouokay-2 is a Rhat plot. It shows... This suggests... -->
